Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-23 WSSSPE4_report/WSSSPE4_report.tex
working on open research index section of report

@@

>>>>

In each group's discussion, a number of Specific, Measurable, Achievable, Relevant and Timely (SMART) steps were created, and ideally, at least the first one (to set up some communication mechanism) was completed.  In many cases, this was done through Slack (see \S\ref{sec:slack}.)

@@

\section{Slack team and channels}\label{sec:slack}

As part of the discussion at WSSSPE4, we created a Slack team for WSSSPE.  To join it, go to \url{https://wssspe.signup.team/}.  A number of the working groups also created channels within the team; see the subsections in \S\ref{sec:WGs} for the names of these channels.

### 2016-11-23 WSSSPE4_report/wg_open_research_index.tex
working on open research index section of report

Names of people willing to contribute (or expertise needed), and how they?ll contribute
- Could bring in someone from ORCID, CrossRef, DataCite, ImpactStory/depsy, altmetrics.org, Plum Analytics, GitHub, Open AIRE, CHORUS, FORCE11, COS, SHARE, CASRAI, Portico, softwareheritage.org, DBLP, eSTEP (CWO)
- Work with some initial publishers who don?t have competing services (domain societies), PubMed, 
- Need to discuss with potential funders
   - What data/services would they like to have
      - Are they willing to invest in this?
      - E.g. current Arnold Foundation Open Science call
- Who would actually lead and coordinate this activity?

What external resources are needed, and how they can be brought in?
- Money
- Time

@@

Currently unclear if any of us have the time/energy to pursue this

If we do, plan could be:
- Obtain funding for conversations
- Conversations with potential partners (publishers, orgs, funders) (could be combined with meeting below)
- Conversation with Google Scholar developer for better understanding of what they did and are doing
- Funding for a meeting (perhaps from NSF) (Dagstuhl meeting?)
- Meeting to define a plan
- Funding to implement the plan

Could also build a mailing list for us and discuss further, depending on how receptive others are to this idea

Possible Plans

@@

What are the first SMART steps proposed?

Community mailing list/forum (Kyle, today)
done - wg-open-research-idx on wssspe slack channel

@@

Apply for initial funding
- For the US, consider Arnold Foundation Open Science award as a planning activity (who, due Dec 15)
- For the UK,

@@

\subsubsection{More information \& joining instructions}

How could a reader get more information or get more involved?

add into about joining WSSSPE slack and then this channel.

>>>>

People/organizations who might be willing to contribute (or whose expertise is needed), and how they will contribute:

\begin{itemize}
\item ORCID, CrossRef, DataCite, ImpactStory/depsy, altmetrics.org, Plum Analytics, GitHub, Open AIRE, CHORUS, FORCE11, COS, SHARE, CASRAI, Portico, softwareheritage.org, DBLP, eSTEP (CWO)
\item We could work with some initial publishers who don't have competing services (domain societies), PubMed
\item We need to discuss this idea with potential funders, and ask what data/services would they like to have?  And are they willing to invest in this?
\end{itemize}

The external resources that are needed are money and time; it is unclear how they can be brought in.

@@

At the time of the meeting, and today as well, it is unclear who has the time and energy to pursue this idea.

If we identify a leader (PI), a plan could be:
\begin{enumerate}
\item Obtain funding for a set of initial discussions (or find a group who feel that this is important enough that they will take the time to do it anyhow)
\item Talk with potential partners (publishers, orgs, funders) (could be combined with meeting below)
\item Talk with the Google Scholar developer for better understanding of what they did and are planning in the future
\item Obtain funding for a meeting (perhaps from NSF, perhaps a Dagstuhl meeting)
\item Hold a community meeting to define a plan (which should be large enough to include representative of all stakeholder groups, and small enough that we still have a good open discussion)
\item Obtain funding to implement the plan, including contributions and commitments from the stakeholders
\end{enumerate}

Alternatively or additionally, we could build a mailing list for us and discuss further, depending on how receptive others are to this idea.  At WSSSPE4, there seemed to be enough interest to do this, so we set up a Slack channel within the WSSSPE team, called \#wg-open-research-idx.  (See \S\ref{sec:slack} to join the Slack WSSSPE team.)

\paragraph{Possible Plans}

@@

The working group discussed a number of SMART steps, though most of them did not fulfill all the SMART criteria:

\begin{enumerate}
\item Develop a community mailing list/forum (Kyle, during the workshop).  This was completed; see \S\ref{sec:wg-open-research-index-list}.

@@

Apply for initial funding
- For the US, consider Arnold Foundation Open Science award as a planning activity (who, due Dec 15)
- For the UK, ?

@@

\end{enumerate}

\subsubsection{More information \& joining instructions}\label{sec:wg-open-research-index-list}

If you are interested in more information, please join the WSSSPE team's Slack channel for this working group: \#wg-open-research-idx.  (See \S\ref{sec:slack} to join the Slack WSSSPE team.)
